### 2015-12-10 ML/hw8/hw.tex
final version hw8 ML

The k-nearest neighbours algorithm in the feature space by introducing the feature map is

@@

In order that it only depends on the scalar product in feature space $K(\phi(x),\phi(x^{(s_i)})) = \phi(x)^T\phi(y)$, we square this. Using that operation, the k-nearest neighbours don't change.

@@

\begin{align}
(1-\alpha)f_{\lambda '}(x) + \alpha f_{\lambda '}(y) \geq& f_{\lambda '}(1-\alpha)x + \alpha y)\\
=& \max\limits_{\lambda}f_\lambda((1-\alpha)(x + \alpha y).
\end{align}

\section*{Problem 4}
The Lagrangian is given by

\begin{equation}
L(x,\alpha) = f_0(x) + \sum_{i}{\alpha_i f_i(x)}.
\end{equation}

This can also be interpreted as a family of functions $L_x(\alpha) = L(x,\alpha)$, that means we interpret $x$ as fixed. Thus $L_x(\alpha)$ has the form

\begin{equation}
L_x(\alpha) = C_{0,x} + \sum_{i}{C_{i,x} \alpha_i},
\end{equation}

where the $Cs$ are constants. By applying the definition of a convex function we see immediately that $L_x(\alpha)$ is convex for any $Cs$.
The Lagrange dual function is given by the pointwise minimum of this family of functions,

@@

The negative Lagragian $-L_x(\alpha)$ is also convex, because the negation only changes the sign of the
constants $C_{0,x}$ and $C_{i,x}$. Thus, as shown in the previous exercise,$-g(\alpha)$ is convex and $g(\alpha)$ is concave.

>>>>

The distance to a training sample in feature space is given by

@@

In order that it only depends on the scalar product in feature space $K(x, x^{(s_i)}) = \phi(x)^T\phi(y)$, we square this. Using that operation, the k-nearest neighbours don't change.

@@

\begin{align}
(1-\alpha)f_{\lambda '}(x) + \alpha f_{\lambda '}(y) \geq& f_{\lambda '}(1-\alpha)x + \alpha y)\\
=& \max\limits_{\lambda}f_\lambda((1-\alpha)(x + \alpha y).
\end{align}s

@@

The negative Lagragian $-L_x(\alpha)$ is also convex, because the negation only changes the sign of the
constants $C_{0,x}$ and $C_{i,x}$. Thus, as shown in the previous exercise,$-g(\alpha)$ is convex and $g(\alpha)$ is concave
